%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[margin, 11pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage[colorlinks = true,
linkcolor = blue,
urlcolor = blue,
citecolor = blue,
anchorcolor = blue]{hyperref}

%\usepackage{hyperref}

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

    \moveleft.5\hoffset\centerline{\huge\textbf{Michael Theodorides}}

    \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt} %\smallskip

    \begin{resume}

        %\section{OBJECTIVE}

        %Talented young engineer looking to work in a team of hackers, that are passionate about their code.
        %I don't mind new challenges; late night coding sessions; or freaked out customers; i just want it to be fun, and meaningful.

        \section{ABOUT ME}\label{sec:aboutme}

        Experienced and versatile software engineer with over a decade of hands-on experience in backend and full-stack development, working with modern technologies across a wide range of projects and teams. Agile, fast-learning, and collaborative by nature, I thrive in dynamic environments and bring a pragmatic, solution-driven mindset to every challenge. I take pride in writing clean, maintainable code and contributing to products that make a real impact. Fluent in English and Greek (native), with very good knowledge of Russian. I'm passionate about sharing knowledge and helping teams level up by drawing on my experience and technical insight. \\

        \section{EXPERIENCE}\label{sec:experience}

        \textsc{ \textbf{Work}}

        \begin{itemize}
            \item[Sep 2023 - present] Senior Backend software engineer at \href{https://exness.com}{exness.com}.
            Working with Python, Postgres, Redis, kubernates, Vertica, Clickhouse

            
            \item[Nov 2021 - Sep 2023] Senior full stack engineer at \href{https://bdswiss.com}{bdswiss.com}.
            Working with React, Graphql, Nodejs, Postgres, and Redis

            \item[Feb 2019 - Oct 2021] Senior full stack engineer at \href{http://prixie.net}{prixie.net}.
            Working with Angular, Cypress, Nodejs, NWjs, Python, Docker, Mongo, Mysql, Redis, ELK, and RethinkDb

            \item[Sep 2018 - Feb 2019] Senior frond end engineer at \href{http://impactechs.com}{impactechs.com}.
            Working with Angular, Protractor, Docker

            \item[Feb 2018 - Sep 2018] Full stack team leader at cs circles solutions.
            Working with Angular, Protractor, Ionic, Nodejs, Jest, Docker, GO, CouchDB, and Redis

            \item[Jul 2016 - Feb 2018] Full stack web engineer at cs circles solutions.
            Working with Angular, Nodejs, and GO

            \item[Dec 2014 - Jul 2016] Full stack web engineer at \href{https://proto.io/}{proto.io}.
            Working with Vanilla JavaScript, Nodejs, and Redis

            \item[Summer 2012 intern] Junior C\#(WPF, WCF) software engineer in mobility devision at \href{http://www.datatech.com.cy/}{datatech.com.cy}.

        \end{itemize}


        \section{PERSONAL \\ INFORMATION}\label{sec:personalinformation}

        \begin{tabular}{p{0.2\linewidth} p{0.75\linewidth}}

            Date of birth & August 31st, 1990                               \\
            Nationality & Greek                                             \\
            Email & mc.theodorides@gmail.com                                \\
            Phone Nu. & (+357)99112779                                      \\
            Address & Iktinou 24, fl. 609, 3075 Limassol Cyprus.

        \end{tabular}\\

        \section{EDUCATION}\label{sec:education}

        Bachelor in electrical engineering, computer engineering and informatics, \\
        from Cyprus university of technology. \\

    \end{resume}
\end{document}
